### 2022-02-10 chapters/drto/article.tex
last chapter added to manuscript
appendices added to manuscript

\begin{figure}
    \centering
    \includegraphics[width=.9\textwidth]{chapters/drto/figures/fig4.jpg}
    \caption{ (a) Vulnerability indicator value of all sub-reefs of the DRTO in November 2020. Eastern reefs of the DRTO appear most vulnerable to the disease. Locations where the SCTLD was observed in the DRTO are indicated by red stars (b) Source indicator value in November 2020 for every sub-reef of the Marquesas and the Western Marquesas. Northwestern reefs of the Western Marquesas and southern reefs between the Marquesas and the Western Marquesas show a higher transmission potential to the DRTO. Main islands are shown in dark grey, separation between the Marquesas and the Western Marquesas is indicated by a dashed line.}
    \label{fig:fig4_drto}
\end{figure}

@@

>>>>

\begin{figure}
    \centering
    \includegraphics[width=.9\textwidth]{chapters/drto/figures/fig4.png}
    \caption{ (a) Vulnerability indicator value of all sub-reefs of the DRTO in November 2020. Eastern reefs of the DRTO appear most vulnerable to the disease. Locations where the SCTLD was observed in the DRTO are indicated by red stars (b) Source indicator value in November 2020 for every sub-reef of the Marquesas and the Western Marquesas. Northwestern reefs of the Western Marquesas and southern reefs between the Marquesas and the Western Marquesas show a higher transmission potential to the DRTO. Main islands are shown in dark grey, separation between the Marquesas and the Western Marquesas is indicated by a dashed line.}
    \label{fig:fig4_drto}
\end{figure}

@@

\begin{subappendices}
	\section{Validation of the model}

	SLIM outputs were validated against field measurements from tide gauges and ADCP in the Florida Keys and on the shelf (Fig. \ref{fig:a1}). Here, we show the comparison between observed and simulated sea surface elevation and current speed for the month of November 2020. The model accurately reproduces the observed sea surface elevation at all tide gauges (Fig. \ref{fig:a2}) with an RMSE of less than 8 cm. The current velocity on the shelf is also  well reproduced by the model, despite a slight underestimation of the southward component of the observed currents at mooring C10 and C22, located on the 25 m and 70 m isobaths respectively (Fig. \ref{fig:a3}). Using the vector correlation analysis of \citep{kundu1976ekman}, we obtained a correlation factor of 0.9 and a veering angle of 10$^\circ$ between the modeled currents and the observations at station C10. A correlation factor of 0.75 and a veering angle of 8° were obtained at mooring C22. Such values are similar to the performances of previous modeling studies on the West Florida Shelf \cite{liu2020impacts}.

	\begin{figure}
		\centering
		\includegraphics[width=.8\textwidth]{chapters/drto/figures/a1.JPEG}
		\caption{Mesh of the computational domain with the location of the stations used for the validation of the model outputs. Land is shown in dark gray.}
		\label{fig:a1}
	\end{figure}

	\begin{figure}
		\centering
		\includegraphics[width=\textwidth]{chapters/drto/figures/a2.png}
		\caption{Comparison of SLIM sea surface elevation against tide gauge elevation in November 2020. The tidal signal is well reproduced at all stations with an RMSE of less than 8 cm.}
		\label{fig:a2}
	\end{figure}

	\begin{figure}
		\centering
		\includegraphics[width=\textwidth]{chapters/drto/figures/a3.png}
		\caption{Comparison of SLIM currents with depth-averaged ADCP measurements at mooring C10 and C22 in November 2020. Despite a slight underestimation of their southward component, currents and their oscillations are well reproduced by the model.}
		\label{fig:a3}
	\end{figure}

	SLIM relies on its coupling with HYCOM GoM to accurately reproduce the Loop Current (LC)-Florida Current (FC) system. HYCOM’s surface fields were therefore compared with sea surface temperature data from the Group for High Resolution Sea Surface Temperature (GHRSST; \url{https://www.ghrsst.org/}). HYCOM reproduces well the penetration of the LC in the Gulf of Mexico (Fig. \ref{fig:a4}), which is key to simulating the eddy activity linked to the meandering of the FC near the DRTO.

		\begin{figure}
		\centering
		\includegraphics[width=\textwidth]{chapters/drto/figures/a4.JPEG}
		\caption{Comparison of (\textbf{A}) satellite-derived sea surface temperature from the Group for High Resolution Sea Surface Temperature (GHRSST) against (\textbf{B}) sea surface temperature, (\textbf{C}) sea surface height (SSH) and (\textbf{D}) surface current magnitude modeled by HYCOM. All panels are snapshots of November 15, 2019 at 0000 UTC.  The model reproduces well the penetration of the LC in the Gulf of Mexico.}
		\label{fig:a4}
	\end{figure}

\end{subappendices}
